A New Metric for the Analysis of Swarms using Potential Fields

### 2018-08-06 paper.tex
More Updates

>>>>

This paper builds upon the work relating to the \textit{Magnitude-based} metric analysis as discussed by Bennet and McInnes and Wu et al. by expanding the analysis to the entire swarm and converting the magnitudes to a scalar value so that the metric produces an arbitrary value that can be used to compare swarm algorithms.
